Dear Members of the Turing Award Committee,

I am honored to nominate Professor Todd Millstein, Chair of the Computer Science Department at the University of California, Los Angeles, for the ACM Turing Award. Professor Millstein’s transformative contributions to the field of programming languages and software engineering have had a profound impact on both the theoretical foundations and practical applications of computing. His work exemplifies the principles of innovation, rigor, and societal benefit that the Turing Award celebrates.

Professor Millstein is widely recognized for his pioneering research in program analysis, type systems, and formal verification. Through groundbreaking studies, he has advanced our understanding of how to create reliable, efficient, and secure software systems. His early contributions to the development of scalable static analysis frameworks demonstrated the potential to detect subtle programming errors automatically, influencing the design of many modern software tools used in industry today.

A key highlight of Professor Millstein’s career is his work on [specific achievement, e.g., "co-developing the concept of 'demand-driven program analysis,' which revolutionized how developers identify performance bottlenecks in large-scale systems"]. His approach combined rigorous formal methods with practical utility, bridging the gap between academia and real-world software development. These innovations have become essential in ensuring software correctness and safety in critical domains such as autonomous systems, cloud computing, and cybersecurity.

In addition to his technical contributions, Professor Millstein is a dedicated mentor and educator. His commitment to fostering new generations of computer scientists has shaped the careers of countless students, many of whom have gone on to achieve distinction in academia and industry. As department chair, he has championed initiatives that promote diversity, interdisciplinary research, and the broader integration of computer science into addressing societal challenges.

For his outstanding contributions to the field and his enduring legacy, I wholeheartedly recommend Professor Todd Millstein for the ACM Turing Award. 